\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
\newcommand{\researchAssistant}[1]{\textbf{Research Assistant (RA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Farshad Koohifar}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{www.koohifar.com}
% vs how you want it to show up. If it's you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://koohifar.com}
\newcommand{\yourEmail}{farshad.koohifar@gmail.com}
\newcommand{\yourPhone}{1-786-315-7145}
\newcommand{\githubUserName}{FarshadKoohifar}
\newcommand{\linkedInUserName}{farshad-koohifar-35667863}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Large \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}

\resumeHeading{Modern Hire}{Machine Learning Engineer II}{Austin, Tx}{Feb 2021 – present}
\begin{bullets}
\justifying
    \item Tech lead for \textbf{Continuous Monitoring} of our production models and transcription pipeline through \textbf{AWS SES} and \textbf{Snowflake} datamarts. This system continuously monitors for abnormal population drift and abnormal empirical prediction histograms through \textbf{Stochastic Time Series} modeling of the expected observations.
    \item Tech lead for \textbf{Occupational AI}, which clusters similar occupations based on job descriptions using \textbf{BERTopic}, resulting in improved default configuration of new job openings. This project is still in progress and is expected to significantly reduce the required resources for onboarding new clients.
    \item Designed and implemented multilingual heteroskedastic \textbf{Transformer} based \textbf{NLP} models using \textbf{Torch} and \textbf{HuggingFace} to predict 11 behavioural metrics. Our published results outperformed our competition.
    \item Designed and implemented a \textbf{Tabular Ensemble Learning} model that predicts the job performance and turn over, using pre-hire assessment data. This is used to provide our clients with an estimate of monetary value of our services.

\end{bullets}

\resumeHeading{Modern Hire}{Machine Learning Engineer}{Austin, Tx}{Oct 2019 – Feb 2021}
\begin{bullets}
\justifying
    \item Designed and implemented a \textbf{Scalable}, \textbf{Distributed} and \textbf{Fault Tolerant} hyperparameter tuning and model training infrastructure with real time worker status monitoring and report generation using \textbf{Python}:
    \begin{bullets}
        \item Asynchronous scaling through \textbf{AWS EC2}, \textbf{AWS S3}, and \textbf{AWS ECR}.
        \item Saving 70\% of the time spent on infrastructure provisioning from 20 minutes to 6 minutes spent per job.
    \end{bullets}
    \item Designed and implemented \textbf{LSTM} based \textbf{NLP} models and compared their performance with \textbf{Transformer} based models. As a result, the product technology road map switched to \textbf{RoBERTa} and later to \textbf{XlmRoBERTa}.
    \item Designed and implemented a mask based \textbf{Model Explainability} tool that enables us to generate heat maps for \textbf{Transformer} based models and most important word clusters, the most requested features from our clients.
    \item Designed and implemented a \textbf{CNN} image processing model to predict applicants' race and gender based on their video interviews, ensuring that our models were unbiased and remain unbiased against protected classes.
\end{bullets}

\resumeHeading{Modern Hire}{Machine Learning Intern}{Raleigh, Nc}{Jul 2019 – Oct 2019}
\begin{bullets}
\justifying
    \item Designed and implemented audio processing deep learning models to predict verbal expression of our applicants based on \textbf{FastAI}. The models match human experts correlation with expert consensus on verbal expression.
    \item Designed and implemented 7 \textbf{audio feature extraction} methods including: Pitch, Pace, Intensity, and Hesitation. We showed significant correlation between pace and on the job performance for bank tellers.
\end{bullets}

\resumeHeading{DARPA}{Spectrum Collaboration Grand Challenge}{Raleigh, Nc}{Oct 2017 – Jul 2019}
\begin{bullets}
\justifying
    \item I led team Wolfpack, North Carolina State University's team of three, that became \textbf{Phase I and Phase II finalist} for DARPA SC2 Grand Challenge, leading to a \textbf{\$150,000 award and recognition from National Science Foundation}.
    \item We designed a distributed and fault tolerant collaborative communication network with high computation and spectrum efficiency using \textbf{C++} and \textbf{Python}.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{Ph.D. Electrical and Computer Engineering}{North Carolina State University}{Raleigh, NC}{Aug 2021}\\
\researchAssistant{Cognitive Networks}\\
\educationHeading{M.S. Electrical and Computer Engineering}{Sharif University of Technology}{Tehran, Iran}{Aug 2013}\\
\teacherAssistant{Intelligent Systems Lab}\\
\educationHeading{B.S. Electrical and Computer Engineering}{Iran University of Science and Technology}{Tehran, Iran}{Sep 2011}\\
\teacherAssistant{Advanced Networking}\\
% \courseWork{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{Python, C++, SQL, Matlab, \LaTeX}\\
    \singleItem{Machine Learning:}{Transformers, CNN, LSTM, SVM, KNN, Naive Bayes}\\
    \singleItem{Packages:}{Pandas, Torch, Numpy, SciKitLearn, Matplotlib, Seaborn}\\
    \singleItem{Technology:}{AWS, Docker, Git, Flask, Fastai}
\end{skillList}

\end{document}